---
title: "Build ACS and UCR Predictor Data"
format: html
---

## American Community Survey

The American Community Survey is the annual survey conducted by the US Census Bureau that collects detailed socioeconomic and demographic data. The 5-year estimates are utilised in this study. The ACS provides estimates rather than hard counts and so includes a margin of error. 

```{r acs-vars}
# Variables
acs_vars <- c(
  # demographic
  total_pop = "B01003_001",
  white_non_hisp = "B03002_003",
  black_non_hisp = "B03002_004",
  hispanic_pop = "B03003_003",
  foreign_born = "B05002_013",
  # socioeconomic
  med_income = "B19013_001",
  poverty_count = "B17001_002",
  gini = "B19083_001",
  high_school = "B15003_017",
  bachelor_deg = "B15003_022",
  pop_over_25 = "B15003_001",
  pt_to_work = "B08006_008",
  commuters_total = "B08006_001",
  uninsured = "S2701_C04_001",
  civ_pop = "S2701_C01_001",
  # property
  total_properties = "B25003_001",
  renter_units = "B25003_003",
  med_home_val = "B25077_001"
)

# ACS data, 5-year values
acs_raw <- get_acs(
  geography = "county",
  variables = acs_vars,
  year = 2024,
  output = "wide",
  geometry = TRUE,
  cb = FALSE
)
```

### Data Cleaning

```{r acs-cleaning}
acs <- acs_raw |> 
  mutate(
    p_black      = black_non_hispE / total_popE,
    p_hisp       = hispanic_popE / total_popE,
    p_white      = white_non_hispE / total_popE,
    poverty_rate = poverty_countE / total_popE,
    p_renter     = renter_unitsE / total_propertiesE,
    p_foreign    = foreign_bornE / total_popE,
    pop_den      = total_popE / (as.numeric(st_area(geometry)) / 1000000), # persons per km²
    log_pop_den  = log1p(pop_den),
    p_edu_hs     = high_schoolE / pop_over_25E, # education is measured as "highest level of education achieved"
    med_income   = med_incomeE / 10000,      # in units of $10,000
    med_home_val = med_home_valE / 10000,     # in units of $10,000
    p_edu_ba     = bachelor_degE / pop_over_25E,
    p_pt_to_work = pt_to_workE / commuters_totalE,
    p_uninsured  = uninsuredE / civ_popE
  ) |> 
  select(
    GEOID, NAME, total_popE,
    p_black, p_hisp, p_white, p_foreign,
    med_income, giniE, med_home_val,
    p_renter, poverty_rate,
    p_edu_hs, p_edu_ba,
    pop_den, log_pop_den, geometry, p_pt_to_work, 
    p_uninsured
  ) |> 
  rename(
    total_pop = total_popE,
    gini = giniE,
  )

# High-Level Summary
skim(acs)
```

### Crime Rate

Data from the FBI's 'Return A' was used as a control. This data was downloaded from professor Jacob Kaplan's Concatenated Files (https://www.icpsr.umich.edu/sites/icpsr/view/studies/100707/versions/V22) which is pre-cleaned and includes FIPs codes. The data is provided at the agency level, so was aggregated to the county level.

```{r documented-acquisition}
atlas |>
  filter(!is.na(year), year >= 2000, year <= 2025) |>
  count(year) |>
  ggplot(aes(x = year, y = n)) +
  annotate("rect",
    xmin = 2014, xmax = 2018, ymin = -Inf, ymax = Inf,
    fill = "steelblue", alpha = 0.12
  ) +
  geom_line(linewidth = 0.8, colour = "grey20") +
  geom_point(size = 1.5, colour = "grey20") +
  annotate("text",
    x = 2016, y = Inf, label = "Crime rate\naveraging window",
    vjust = 1.3, size = 3, colour = "steelblue4"
  ) +
  labs(
    title    = "Documented technology acquisitions over time",
    subtitle = "Proxy: year of first published article about acquisition | shaded band = crime/officer rate averaging window (2014–2018)",
    x = NULL, y = "New records (all technologies combined)"
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Times New Roman"),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14, colour = "grey40"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    panel.background = element_rect(fill = "grey90", colour = NA),
    plot.background = element_rect(fill = "white", colour = NA),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white")
  )
```

```{r crime-data}
crime_raw <- read_csv("data/offenses_known_yearly_1960_2024.csv")

# Inspect
glimpse(crime_raw)
```

```{r crime-data-names}
names(crime_raw)
```

```{r crime-fips-check}
# Check FIPS
crime_raw |> select(matches("fips|county|geoid", ignore.case = TRUE)) |> head()
crime_raw |> select(fips_state_county_code) |> distinct() |> head(10)
```

```{r county-aggregation}
# Aggregate agency-level data to county-year, then average across years
crime_county_year <- crime_raw |>
  filter(
    year >= 2014, year <= 2018,                # pre-dates most Atlas acquisitions (mean ~2018)
    number_of_months_reported >= 10             # exclude agencies with substantial partial-year gaps
  ) |>
  mutate(GEOID = str_pad(as.character(fips_state_county_code), width = 5, side = "left", pad = "0")) |>
  group_by(GEOID, year) |>
  summarise(
    total_violent  = sum(actual_index_violent,  na.rm = TRUE),
    total_property = sum(actual_index_property, na.rm = TRUE),
    total_crime    = sum(actual_index_total,    na.rm = TRUE),
    population     = sum(population, na.rm = TRUE),   # sum across multiple agencies covering the same county
    .groups = "drop"
  ) |>
  filter(population > 0) |>   # avoid divide-by-zero for counties with no reporting agency that year
  mutate(
    violent_rate  = log1p(total_violent  / population * 100000),
    property_rate = log1p(total_property / population * 100000),
    crime_rate    = log1p(total_crime    / population * 100000)
  )

# ── Average across the 5-year window per county ──
crime_county_avg <- crime_county_year |>
  group_by(GEOID) |>
  summarise(
    mean_violent_rate  = mean(violent_rate,  na.rm = TRUE),
    mean_property_rate = mean(property_rate, na.rm = TRUE),
    mean_crime_rate     = mean(crime_rate,    na.rm = TRUE),
    n_years_reported    = n(),
    .groups = "drop"
  )

```

### Sworn Officers

Data from the FBI's Law Enforcement Employees dataset as concatenated into Professor Jacob Kaplan's LEOKA dataset (https://www.openicpsr.org/openicpsr/project/102180/version/V15/view?path=/openicpsr/102180/fcr:versions/V15/LEOKA_csv_1960_2024_year.zip&type=file) was used to extract the number of sworn officers in each county. 

```{r officers-data}
officers_raw <- read_csv("data/leoka_yearly_1960_2024.csv")

# Aggregation
officers_county_year <- officers_raw |>
  filter(
    year >= 2014, year <= 2018,
    number_of_months_reported >= 10
  ) |>
  mutate(GEOID = str_pad(as.character(fips_state_county_code), width = 5, side = "left", pad = "0")) |>
  group_by(GEOID, year) |>
  summarise(
    total_sworn_officers = sum(total_employees_officers, na.rm = TRUE),
    total_civilians       = sum(total_employees_civilians, na.rm = TRUE),
    population            = sum(population, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(population > 0) |>
  mutate(
    officers_per_1000 = log1p(total_sworn_officers / population * 1000),
    civilian_share     = total_civilians / (total_sworn_officers + total_civilians)
  )

officers_county_avg <- officers_county_year |>
  group_by(GEOID) |>
  summarise(
    mean_officers_per_1000 = mean(officers_per_1000, na.rm = TRUE),
    mean_civilian_share    = mean(civilian_share,     na.rm = TRUE),
    n_years_reported       = n(),
    .groups = "drop"
  )

# Coverage check, same pattern as crime rate
officers_county_avg |> count(n_years_reported)
```

`crime_county_avg` and `officers_county_avg` are joined onto the modelling
dataset in `06_models_main.qmd`, once `spatial_df_extended` exists. See
"Merge Crime and Officer Controls" there.
