---
title: "Exploratory Analysis"
format: html
---

## Exploratory Analysis

### Atlas of Surveillance

#### Technology Distribution

```{r}
# Count and share of each technology type
tech_counts <- atlas |>
  count(technology, sort = TRUE) |>
  mutate(
    pct   = n / sum(n),
    technology = fct_reorder(technology, n)
  )

ggplot(tech_counts, aes(x = n, y = technology)) +
  geom_col(fill = "#4C72B0") +
  geom_text(aes(label = scales::percent(pct, accuracy = 0.1)),
            hjust = -0.1, size = 3) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.12))) +
  labs(
    title    = "Atlas of Surveillance: technology frequency",
    subtitle = paste0("n = ", scales::comma(nrow(atlas)), " records"),
    x = "Count", y = NULL
  ) +
  theme_minimal()
```

#### Agency

```{r}
atlas |>
  count(lea_type, sort = TRUE) |>
  mutate(lea_type = fct_reorder(lea_type, n)) |>
  ggplot(aes(x = n, y = lea_type)) +
  geom_col(fill = "#696FC7") +
  labs(title = "Records by law enforcement agency type",
       x = "Count", y = NULL) +
  theme_minimal()
```

#### –> How to delegate larger agencies like state police, district attorney, and prosecutor’s office into the county level?

#### State-level Distribution

```{r}
state_coverage_plot <- atlas |>
  count(state, state, sort = TRUE) |>
  mutate(state = fct_reorder(state, n)) |>
  ggplot(aes(x = n, y = state)) +
  geom_col(fill = "#332288") +
  labs(title = "States by number of surveillance records",
       x = "Count", y = NULL) +
  theme_thesis(base_size = figure_base_size - 6)

save_figure(state_coverage_plot, "state_coverage_plot.png", width = 8, height = 7)
```

```{r}
state_coverage_plot
```

#### Vendors

```{r}
# Top 15 vendors
atlas |>
  filter(!is.na(vendor)) |>
  count(vendor, sort = TRUE) |>
  slice_head(n = 15) |>
  mutate(vendor = fct_reorder(vendor, n)) |>
  ggplot(aes(x = n, y = vendor)) +
  geom_col(fill = "#DD8452") +
  labs(title = "Top 15 surveillance vendors",
       x = "Records", y = NULL) +
  theme_minimal()
```

```{r}
# Vendors by technology type
atlas |>
  filter(!is.na(vendor)) |>
  group_by(technology) |>
  count(vendor, sort = TRUE) |>
  slice_max(n, n = 3) |>       # top 3 vendors per tech
  ungroup()
```

#### Temporal Trends

```{r}
# Adoptions per year, faceted by technology
# Note: date = date of first published article, not confirmed acquisition date
atlas |>
  filter(!is.na(year), year >= 2000, year <= 2025) |>
  count(year, technology) |>
  ggplot(aes(x = year, y = n, colour = technology)) +
  geom_line() +
  geom_point(size = 1) +
  facet_wrap(~ technology, scales = "free_y") +
  labs(
    title    = "Technology adoption over time",
    subtitle = "Proxy: year of first published article about acquisition",
    x = NULL, y = "New records", colour = NULL
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

```{r}
# Aggregate annual trend
atlas |>
  filter(!is.na(year), year >= 2000, year <= 2025) |>
  count(year) |>
  ggplot(aes(x = year, y = n)) +
  geom_col(fill = "#4C72B0") +
  labs(title = "Total surveillance technology acquisitions by year",
       subtitle = "All technology types combined",
       x = NULL, y = "Records") +
  theme_minimal()
```

#### Technology co-occurrence per county

```{r}
atlas |>
  group_by(state, county) |>
  summarise(
    n_records  = n(),
    n_tech_types = n_distinct(technology),
    .groups = "drop"
  ) |>
  ggplot(aes(x = n_tech_types)) +
  geom_histogram(binwidth = 1, fill = "#4C72B0", colour = "white") +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  labs(
    title = "Distribution of distinct technology types per county",
    x = "Number of distinct technologies", y = "Count of counties"
  ) +
  theme_minimal()
```

### ACS

```{r}
# spatial_df |>
#   st_drop_geometry() |>
#   filter(if_any(c(p_black, p_hisp, p_foreign, med_income, gini, log_pop_den), is.na))
```

```{r}
# Basic checks
glimpse(acs)
```

```{r}
summary(acs)
```

```{r}
# County size
acs |> slice_max(total_pop, n = 10)
```

```{r}
# Missing values
acs |>
  st_drop_geometry() |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") |>
  filter(n_missing > 0)
```

#### Distributions

```{r}
numeric_vars <- acs |> 
  st_drop_geometry() |>
  select(where(is.numeric)) |>
  names()

acs |>
  st_drop_geometry() |>
  select(all_of(numeric_vars)) |>
  pivot_longer(everything(), names_to = "variable", values_to = "value") |>
  ggplot(aes(x = value)) +
  geom_histogram(bins = 40, fill = "#696FC7", colour = "white", linewidth = 0.2) +
  facet_wrap(~ variable, scales = "free") +
  labs(title = "Distribution of key ACS variables", x = NULL, y = "Count") +
  theme_minimal()
```

#### Predictor Correlation Matrix

```{r}
cor_data <- acs |>
  st_drop_geometry() |>
  select(all_of(numeric_vars)) |>
  drop_na()

# Plot 
ggcorr(cor_data, 
       method = c("everything", "pearson"), 
       digits = 2,              # decimal places
       label = TRUE, 
       label_size = 3, 
       label_round = 2,         # rounding to two places
       hjust = 0.85,            # Adjusted for label alignment
       size = 4,                # Overall size of the tiles
       layout.exp = 1,          # Expands the plot area so names aren't cut off
       low = "steelblue", 
       median = "white", 
       high = "tomato") +
  labs(title = "Correlation Matrix: Race and Class Variables",
       subtitle = "Pearson Correlation Coefficients")
```

#### Mapping

```{r}
plot_map <- function(data, var, title, palette = "viridis") {
  ggplot(data) +
    geom_sf(aes(fill = .data[[var]]), colour = NA) +
    scale_fill_viridis_c(option = palette, na.value = "grey80") +
    labs(title = title, fill = NULL) +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"))
}

acs_cont <- acs |>
  filter(!str_detect(GEOID, "^02|^15|^72"))   # drop AK, HI, PR

plot_map(acs_cont, "p_black",     "Proportion Black population")
```

```{r}
plot_map(acs_cont, "p_hisp",      "Proportion Hispanic population")
```

```{r}
plot_map(acs_cont, "med_income",  "Median household income", palette = "plasma")
```

```{r}
plot_map(acs_cont, "poverty_rate","Poverty rate")
```

```{r}
plot_map(acs_cont, "gini",        "Gini coefficient")
```

```{r}
plot_map(acs_cont, "pop_den",     "Population density (per km²)", palette = "plasma")
```

#### Income vs Race

```{r}
acs |>
  st_drop_geometry() |>
  ggplot(aes(x = p_black, y = med_income)) +
  geom_point(alpha = 0.3, size = 0.8) +
  geom_smooth(method = "lm", colour = "firebrick") +
  scale_x_continuous(labels = scales::percent) +
  scale_y_continuous(labels = scales::dollar) +
  labs(
    title = "% Black residents vs. median household income by county",
    x = "Proportion Black", y = "Median income"
  ) +
  theme_minimal()
```

### Correlations

```{r}
analysis_plot <- analysis_df |>
  filter(weighted_index_per100k > 0) |>          # exclude zero-surveillance counties
  mutate(log_index = log1p(weighted_index_per100k))  # log1p = log(x+1), handles zeros safely

# Variables to examine against the surveillance index
acs_predictors <- c(
  "p_black", "p_hisp", "p_white", "p_foreign",
  "med_income", "gini", "med_home_val",
  "poverty_rate", "p_renter",
  "p_edu_hs", "p_edu_ba",
  "log_pop_den", "p_pt_to_work", "p_uninsured" 
)

# Readable labels for plot axes
predictor_labels <- c(
  p_black     = "Proportion Black",
  p_hisp      = "Proportion Hispanic",
  p_white     = "Proportion White",
  p_foreign   = "Proportion Foreign Born",
  med_income  = "Median Household Income",
  gini        = "Gini Coefficient",
  med_home_val = "Median Home Value",
  poverty_rate = "Poverty Rate",
  p_renter    = "Proportion Renter-Occupied",
  p_edu_hs    = "Proportion High School Educated",
  p_edu_ba    = "Proportion Bachelor's Educated",
  pop_den     = "Population Density (per km²)",
  p_pt_to_work = "Proportion Public Transport Commuters",
  p_uninsured = "Proportion Without Health Insurance"
)
```

#### Distribution of Surveillance Index

```{r}
# Raw
p_dist_raw <- analysis_plot |>
  ggplot(aes(x = weighted_index_per100k)) +
  geom_histogram(bins = 50, fill = "#4C72B0", colour = "white", linewidth = 0.2) +
  labs(title = "Distribution of surveillance index (raw)",
       x = "Weighted index per 100,000 population", y = "Count") +
  theme_minimal()

# Log-transformed
p_dist_log <- analysis_plot |>
  ggplot(aes(x = log_index)) +
  geom_histogram(bins = 50, fill = "#696FC7", colour = "white", linewidth = 0.2) +
  labs(title = "Distribution of surveillance index (log-transformed)",
       x = "log(weighted index per 100k + 1)", y = "Count") +
  theme_minimal()

p_dist_raw
```

```{r}
p_dist_log
```

#### Spearman Correlation

```{r}
# Data Preparation
cor_vars <- c("weighted_index_per100k", acs_predictors)

spearman_data <- analysis_df |>
  st_drop_geometry() |>
  filter(weighted_index_per100k > 0) |> # removing counties with no surveillance index 
  select(all_of(cor_vars)) |>
  drop_na()

# Spearman Correlation
spearman_result <- rcorr(as.matrix(spearman_data), type = "spearman")

# Extract correlation coefficients (rho) and p-values
rho_matrix <- spearman_result$r
p_matrix   <- spearman_result$P

# Correlation with Surveillance Index
spearman_summary <- tibble(
  variable = colnames(rho_matrix),
  rho      = rho_matrix["weighted_index_per100k", ],
  p_value  = p_matrix["weighted_index_per100k", ]
) |>
  filter(variable != "weighted_index_per100k") |>
  mutate(
    label          = predictor_labels[variable],
    significant    = p_value < 0.05,
    abs_rho        = abs(rho)
  ) |>
  arrange(desc(abs_rho))

print(spearman_summary, n = Inf)
```

```{r}
# Full Matrix
ggcorr(
  spearman_data,
  method      = c("pairwise", "spearman"),
  digits      = 2,
  label       = TRUE,
  label_size  = 3,
  label_round = 2,
  hjust       = 0.85,
  size        = 3.5,
  layout.exp  = 2,
  low = "steelblue", median = "white", high = "tomato"
) +
  labs(title = "Spearman correlation matrix: surveillance index and ACS predictors")
```

```{r}
# Visualisation
ggplot(spearman_summary, aes(x = rho, y = fct_reorder(label, rho))) +
  geom_segment(aes(x = 0, xend = rho, y = label, yend = label),
               colour = "grey60") +
  geom_point(aes(colour = significant), size = 3) +
  scale_colour_manual(
    values = c("TRUE" = "#4C72B0", "FALSE" = "grey70"),
    labels = c("TRUE" = "p < 0.05", "FALSE" = "n.s."),
    name   = NULL
  ) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey40") +
  labs(
    title    = "Spearman correlation: ACS predictors vs surveillance index",
    subtitle = "Counties with zero surveillance index excluded",
    x = "Spearman's rho", y = NULL
  ) +
  theme_minimal()
```

#### Spatial Autocorrelation

```{r}
# Dataframe
spatial_df <- analysis_df |>
  filter(!st_is_empty(geometry)) |>       
  filter(!is.na(weighted_index_per100k))

# Spatial weights matrix 
# Using Queen contiguity where any counties sharing any point of their border are considered neighbours
neighbours <- poly2nb(spatial_df, queen = TRUE)
summary(neighbours)
```

```{r}
# Check for counties with no neighbours 
no_neighbours <- which(card(neighbours) == 0)
cat("Counties with no neighbours:", length(no_neighbours), "\n")
```

```{r}
spatial_df$NAME[no_neighbours]
```

```{r}
neighbours <- poly2nb(spatial_df, queen = TRUE)
hawaii_idx <- which(str_detect(spatial_df$NAME, "Hawaii"))
# cat("Rows after deduplication: ", nrow(spatial_df), "\n")

# Convert to binary matrix, add Hawaii connections, convert back
nb_mat <- nb2mat(neighbours, style = "B", zero.policy = TRUE)

# Add bidirectional connections between all Hawaii counties
for (i in hawaii_idx) {
  for (j in hawaii_idx) {
    if (i != j) {
      nb_mat[i, j] <- 1
      nb_mat[j, i] <- 1
    }
  }
}

# Convert back to nb object
neighbours_fixed <- mat2listw(nb_mat, style = "W")$neighbours

# Verify using card() on the properly rebuilt object
cat("Counties with no neighbours:", sum(card(neighbours_fixed) == 0), "\n")
```

```{r}
for (i in hawaii_idx) {
  cat(spatial_df$NAME[i], "->",
      paste(spatial_df$NAME[neighbours_fixed[[i]]], collapse = ", "), "\n")
}
```

```{r}
# Rebuild weights
spatial_weights <- nb2listw(neighbours_fixed, style = "W", zero.policy = TRUE)
```

```{r}
build_spatial_weights <- function(df, name_col = "NAME") {
  # Build neighbours from the given spatial dataframe
  nb <- poly2nb(df, queen = TRUE)
  n_isolated_before <- sum(card(nb) == 0)
  
  # Hawaii fix
  hawaii_idx <- which(str_detect(df[[name_col]], "Hawaii"))
  
  if (length(hawaii_idx) > 1) {
    nb_mat <- nb2mat(nb, style = "B", zero.policy = TRUE)
    for (i in hawaii_idx) {
      for (j in hawaii_idx) {
        if (i != j) {
          nb_mat[i, j] <- 1
          nb_mat[j, i] <- 1
        }
      }
    }
    nb <- mat2listw(nb_mat, style = "W", zero.policy = TRUE)$neighbours
  }
  
  n_isolated_after <- sum(card(nb) == 0)
  
  cat("No-neighbour count before Hawaii fix:", n_isolated_before, "\n")
  cat("No-neighbour count after Hawaii fix: ", n_isolated_after, "\n")
  if (n_isolated_after > 0) {
    cat("Remaining isolated counties:\n")
    print(df[[name_col]][card(nb) == 0])
  }
  
  # Final listw object
  nb2listw(nb, style = "W", zero.policy = TRUE)
}
```

##### Moran I Test

```{r}
moran_test <- moran.test(
  log1p(spatial_df$weighted_index_per100k),
  spatial_weights,
  zero.policy = TRUE
)
print(moran_test)
```

```{r}
# Scatterplot
moran.plot(
  log1p(spatial_df$weighted_index_per100k),
  spatial_weights,
  zero.policy = TRUE,
  xlab = "Surveillance index per 100k",
  ylab = "Spatially lagged surveillance index (neighbours' average)",
  main = "Moran scatterplot — surveillance index"
)
```

```{r}
# Local Moran I's (LISA)
lisa <- localmoran(
  spatial_df$weighted_index_per100k,
  spatial_weights,
  zero.policy = TRUE
)

# Add LISA results back to the spatial dataframe
spatial_df <- spatial_df |>
  mutate(
    local_i   = lisa[, "Ii"],      # local Moran's I statistic
    local_p   = lisa[, "Pr(z != E(Ii))"],  # p-value
    local_p_fdr = p.adjust(local_p, method = "fdr"),
    # Classify into cluster types
    index_std  = scale(weighted_index_per100k)[, 1],
    lag_std    = scale(lag.listw(spatial_weights, weighted_index_per100k))[, 1],
    lisa_class = case_when(
      index_std > 0 & lag_std > 0 & local_p_fdr < 0.05 ~ "High-High",
      index_std < 0 & lag_std < 0 & local_p_fdr < 0.05 ~ "Low-Low",
      index_std > 0 & lag_std < 0 & local_p_fdr < 0.05 ~ "High-Low",
      index_std < 0 & lag_std > 0 & local_p_fdr < 0.05 ~ "Low-High",
      TRUE ~ "Not significant"
    )
  )

# Visualisation
lisa_colours <- c(
  "High-High"       = "#d73027",   # red    — surveillance hotspots
  "Low-Low"         = "#4575b4",   # blue   — surveillance coldspots
  "High-Low"        = "#fc8d59",   # orange — high county surrounded by low
  "Low-High"        = "#91bfdb",   # light blue — low county surrounded by high
  "Not significant" = "grey85"
)

spatial_df |>
  filter(!str_detect(GEOID, "^02|^15|^72")) |>   # continental US only
  ggplot() +
  geom_sf(aes(fill = lisa_class), colour = NA) +
  scale_fill_manual(values = lisa_colours, name = "LISA cluster") +
  labs(
    title    = "Local spatial autocorrelation of surveillance index (LISA)",
    subtitle = "High-High = surveillance hotspots; Low-Low = coldspots"
  ) +
  theme_void() +
  theme(
    plot.title    = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 9)
  )
```

```{r}
# Distribution
summary(spatial_df$weighted_index_per100k)
```

```{r}
hist(spatial_df$weighted_index_per100k, breaks = 50)
```

```{r}
# LISA cluster counts and percentages
total_counties <- nrow(spatial_df)

lisa_table <- table(spatial_df$lisa_class)

data.frame(
  cluster    = names(lisa_table),
  n          = as.integer(lisa_table),
  percentage = scales::percent(as.numeric(lisa_table) / total_counties, accuracy = 0.01)
) |>
  arrange(desc(n)) |>
  print(row.names = FALSE)
```

```{r}
lisa_log <- localmoran(
  log1p(spatial_df$weighted_index_per100k),
  spatial_weights,
  zero.policy = TRUE
)

spatial_df <- spatial_df |>
  mutate(
    local_i_log     = lisa_log[, "Ii"],
    local_p_log     = lisa_log[, "Pr(z != E(Ii))"],
    local_p_log_fdr = p.adjust(local_p_log, method = "fdr"),   # <- add this
    index_std_log   = scale(log1p(weighted_index_per100k))[, 1],
    lag_std_log     = scale(lag.listw(spatial_weights, log1p(weighted_index_per100k)))[, 1],
    lisa_class_log  = case_when(
      index_std_log > 0 & lag_std_log > 0 & local_p_log_fdr < 0.05 ~ "High-High",
      index_std_log < 0 & lag_std_log < 0 & local_p_log_fdr < 0.05 ~ "Low-Low",
      index_std_log > 0 & lag_std_log < 0 & local_p_log_fdr < 0.05 ~ "High-Low",
      index_std_log < 0 & lag_std_log > 0 & local_p_log_fdr < 0.05 ~ "Low-High",
      TRUE ~ "Not significant"
    )
  )

# Counts and percentages of log-index LISA 
lisa_log_table <- table(spatial_df$lisa_class_log)
cat("\nLog index LISA:\n")
```

```{r}
data.frame(
  cluster    = names(lisa_log_table),
  n          = as.integer(lisa_log_table),
  percentage = scales::percent(as.numeric(lisa_log_table) / total_counties, accuracy = 0.01)
) |>
  arrange(desc(n)) |>
  print(row.names = FALSE)
```

```{r}
# Visualisation
spatial_df |>
  filter(!str_detect(GEOID, "^02|^15|^72")) |>
  ggplot() +
  geom_sf(aes(fill = lisa_class_log), colour = NA) +
  scale_fill_manual(values = lisa_colours, name = "LISA cluster") +
  labs(
    title    = "LISA clusters — log-transformed surveillance index",
    subtitle = "High-High = hotspots; Low-Low = coldspots"
  ) +
  theme_void() +
  theme(
    plot.title    = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 9)
  )
```

##### Summary

```{r}
cat("Moran's I:  ", round(moran_test$estimate["Moran I statistic"], 4), "\n")
```

```{r}
cat("p-value:    ", round(moran_test$p.value, 6), "\n")
```

```{r}
cat("\nLISA cluster counts:\n")
```

```{r}
print(table(spatial_df$lisa_class_log))
```

#### Scatter Plots

```{r}
# Raw
analysis_plot |>
  st_drop_geometry() |>
  select(weighted_index_per100k, all_of(acs_predictors)) |>
  pivot_longer(-weighted_index_per100k, names_to = "variable", values_to = "value") |>
  mutate(variable = predictor_labels[variable]) |>    # direct lookup, no recode()
  ggplot(aes(x = value, y = weighted_index_per100k)) +
  geom_point(alpha = 0.2, size = 0.6, colour = "#4C72B0") +
  geom_smooth(method = "loess", colour = "firebrick", linewidth = 0.8, se = TRUE) +
  facet_wrap(~ variable, scales = "free_x", ncol = 3) +
  labs(title    = "Surveillance index vs ACS predictors (raw index)",
       subtitle = "Counties with zero surveillance index excluded",
       x = NULL, y = "Weighted index per 100k") +
  theme_minimal() +
  theme(strip.text = element_text(size = 8))
```

```{r}
# Log
analysis_plot |>
  st_drop_geometry() |>
  select(log_index, all_of(acs_predictors)) |>
  pivot_longer(-log_index, names_to = "variable", values_to = "value") |>
  mutate(variable = predictor_labels[variable]) |>
  ggplot(aes(x = value, y = log_index)) +
  geom_point(alpha = 0.2, size = 0.6, colour = "#696FC7") +
  geom_smooth(method = "loess", colour = "firebrick", linewidth = 0.8, se = TRUE) +
  facet_wrap(~ variable, scales = "free_x", ncol = 3) +
  labs(title    = "Surveillance index vs ACS predictors (log-transformed index)",
       subtitle = "Counties with zero surveillance index excluded",
       x = NULL, y = "log(weighted index per 100k + 1)") +
  theme_minimal() +
  theme(strip.text = element_text(size = 8))
```

```{r}
rq_vars <- list(
  list(var = "p_black",            label = "Proportion Black residents",          scale = scales::percent),
  list(var = "p_hisp",             label = "Proportion Hispanic residents",        scale = scales::percent),
  list(var = "p_white",            label = "Proportion White residents",           scale = scales::percent),
  list(var = "p_foreign",          label = "Proportion Foreign Born",              scale = scales::percent),
  list(var = "med_income",         label = "Median household income",              scale = scales::dollar),
  list(var = "poverty_rate",       label = "Poverty rate",                         scale = scales::percent),
  list(var = "gini",               label = "Gini coefficient",                     scale = scales::number),
  list(var = "med_home_val",       label = "Median home value",                    scale = scales::dollar),
  list(var = "p_renter",           label = "Proportion renter-occupied",           scale = scales::percent),
  list(var = "p_edu_hs",           label = "Proportion high school educated",      scale = scales::percent),
  list(var = "p_edu_ba",           label = "Proportion bachelor's educated",       scale = scales::percent),
  list(var = "pop_den",            label = "Population density (per km²)",         scale = scales::comma),
  list(var = "p_pt_to_work",       label = "Proportion public transport commuters",scale = scales::percent),
  list(var = "p_uninsured",        label = "Proportion uninsured",                 scale = scales::percent)
)

for (v in rq_vars) {
  p_raw <- analysis_plot |>
    st_drop_geometry() |>
    ggplot(aes(x = .data[[v$var]], y = weighted_index_per100k)) +
    geom_point(alpha = 0.25, size = 0.8, colour = "#4C72B0") +
    geom_smooth(method = "gam", colour = "firebrick", se = TRUE) +
    scale_x_continuous(labels = v$scale) +
    labs(title = paste("Surveillance index (raw) vs", v$label),
         x = v$label, y = "Weighted index per 100k") +
    theme_minimal()

  p_log <- analysis_plot |>
    st_drop_geometry() |>
    ggplot(aes(x = .data[[v$var]], y = log_index)) +
    geom_point(alpha = 0.25, size = 0.8, colour = "#696FC7") +
    geom_smooth(method = "gam", colour = "firebrick", se = TRUE) +
    scale_x_continuous(labels = v$scale) +
    labs(title = paste("Surveillance index (log) vs", v$label),
         x = v$label, y = "log(weighted index per 100k + 1)") +
    theme_minimal()

  print(p_raw)
  print(p_log)
}
```
