---
title: "Main Models: Selection and Final SARAR Specification"
format: html
---

## Models

### Baseline OLS Model: Raw vs. Logged Index

Two minimal specifications are compared here purely to justify the log
transform used everywhere downstream — this is not a model reported in the
paper. `diagnose_lm()` (defined in `00_setup.qmd`) prints a residuals-vs-fitted
and scale-location plot and returns Cook's D so the two specifications can be
compared without duplicating plotting code.

```{r}
ols_model_raw <- lm(
  weighted_index_per100k ~ p_black + p_hisp + p_foreign +
    med_income + gini + log_pop_den,
  data = spatial_df |> st_drop_geometry()
)

ols_model_log <- lm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign +
    med_income + gini + log_pop_den,
  data = spatial_df |> st_drop_geometry()
)

# Logged specification gives much better-behaved residuals (see plots below),
# so log1p(weighted_index_per100k) is used for every model from here on.
summary(ols_model_log)
```

```{r}
diagnose_lm(ols_model_raw, label = "Raw index")
diagnose_lm(ols_model_log, label = "Logged index")
```

### 3. OLS Additional Predictors (extended)

```{r}
# Extended model: adding median home value and proportion renter 
ols_model_extended <- lm(
  log_index ~ p_black + p_hisp + p_foreign + 
    med_income + gini + med_home_val + p_renter + log_pop_den,
  data = spatial_df |> 
    st_drop_geometry() |> 
    mutate(log_index = log1p(weighted_index_per100k))
)

summary(ols_model_extended)
```

```{r}
car::vif(ols_model_extended)
```

```{r}
# extract_model() is defined once in 00_setup.qmd and reused here and in 07_robustness.qmd
comparison_wide <- bind_rows(
  extract_model(ols_model_log,      "Baseline"),
  extract_model(ols_model_extended, "Extended")
) |>
  mutate(estimate_label = paste0(
    round(estimate, 3),
    case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )) |>
  select(model, term, estimate_label) |>
  pivot_wider(names_from = model, values_from = estimate_label)

model_stats <- tibble(
  model  = c("Baseline", "Extended"),
  adj_r2 = c(glance(ols_model_log)$adj.r.squared, glance(ols_model_extended)$adj.r.squared),
  n      = c(nobs(ols_model_log), nobs(ols_model_extended))
)

comparison_wide
```

```{r}
model_stats
```

```{r}
cooks_d_extended <- diagnose_lm(ols_model_extended, label = "Extended model")
```

## Spatial Weights Updated

```{r}
spatial_df_extended <- spatial_df |>
  filter(!if_any(c(p_black, p_hisp, p_foreign, med_income, gini, log_pop_den, med_home_val, p_renter), is.na))

spatial_weights_extended <- build_spatial_weights(spatial_df_extended)
```

### Rebuild dataset at final population threshold (2,500+)

```{r}
spatial_df_2500 <- spatial_df |> filter(total_pop >= 2500)
weights_2500 <- build_spatial_weights(spatial_df_2500)
```

## Lagrange Multiplier Tests

```{r}
lm_tests_full <- lm.LMtests(
  ols_model_extended,
  spatial_weights,     # <- the renamed listw object, not `weights`
  test = "all",
  zero.policy = TRUE
)

summary(lm_tests_full)
```

### 6. Spatial Lag Model (SAR)

```{r}
sar_model_extended <- lagsarlm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + med_income +
    gini + med_home_val + p_renter + log_pop_den,
  data    = spatial_df_extended |> st_drop_geometry(),
  listw   = spatial_weights_extended,
  zero.policy = TRUE
)

summary(sar_model_extended)
```

```{r}
moran.test(residuals(sar_model_extended), spatial_weights_extended, zero.policy = TRUE)
```

### 7. Spatial Durbin Model (SDM)

```{r}
sdm_model_extended <- lagsarlm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + med_income +
    gini + med_home_val + p_renter + log_pop_den,
  data    = spatial_df_extended |> st_drop_geometry(),
  listw   = spatial_weights_extended,
  zero.policy = TRUE,
  Durbin  = TRUE
)

summary(sdm_model_extended)
```

```{r}
moran.test(residuals(sdm_model_extended), spatial_weights_extended, zero.policy = TRUE)
```

```{r}
LR.Sarlm(sdm_model_extended, sar_model_extended)
```

### 8. SARAR

```{r}
sarar_model_extended <- sacsarlm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + med_income +
    gini + med_home_val + p_renter + log_pop_den,
  data    = spatial_df_extended |> st_drop_geometry(),
  listw   = spatial_weights_extended,
  zero.policy = TRUE
)
summary(sarar_model_extended)
```

```{r}
moran.test(residuals(sarar_model_extended), spatial_weights_extended, zero.policy = TRUE)
```

### Comparison

```{r}
# extract_spatial_model() is defined once in 00_setup.qmd and reused throughout
spatial_comparison <- bind_rows(
  extract_spatial_model(sar_model_extended, "SAR"),
  extract_spatial_model(sdm_model_extended, "SDM")
) |>
  mutate(
    estimate = signif(estimate, 4),
    p_value  = case_when(
      p_value < 0.0005 ~ "< 0.0005",
      TRUE ~ as.character(round(p_value, 4))
    )
  ) |>
  arrange(term, model)

print(spatial_comparison)
```

```{r}
# Model-level comparison: rho, AIC, log-likelihood, residual autocorrelation
model_level_comparison <- tibble(
  model      = c("SAR", "SDM"),
  rho        = c(sar_model_extended$rho, sdm_model_extended$rho),
  rho_pvalue = c(summary(sar_model_extended)$rho.pval, summary(sdm_model_extended)$rho.pval),
  AIC        = c(AIC(sar_model_extended), AIC(sdm_model_extended)),
  logLik     = c(logLik(sar_model_extended), logLik(sdm_model_extended)),
  n          = c(nobs(sar_model_extended), nobs(sdm_model_extended))
)

model_level_comparison
```

```{r}
library(texreg)

screenreg(
  list(
    "SAR"   = sar_model_extended,
    "SDM"   = sdm_model_extended,
    "SARAR" = sarar_model_extended
  ),
  digits = 3,
  include.se = FALSE
)
```

```{r}
htmlreg(
  list("SAR" = sar_model_extended, 
       "SDM" = sdm_model_extended, 
       "SARAR" = sarar_model_extended),
  digits = 3,
  include.se = FALSE,
  file = "figures/sar_sdm_sarar_comparison.html"
)
```

```{r}
# Assumes: sar_model_extended, sdm_model_extended, sarar_model_extended already fit
# on spatial_df_extended / spatial_weights_extended

model_comparison_extended <- tibble(
  model   = c("SAR", "SDM", "SARAR"),
  rho     = c(sar_model_extended$rho, sdm_model_extended$rho, sarar_model_extended$rho),
  lambda  = c(NA, NA, sarar_model_extended$lambda),
  AIC     = c(AIC(sar_model_extended), AIC(sdm_model_extended), AIC(sarar_model_extended)),
  logLik  = c(logLik(sar_model_extended), logLik(sdm_model_extended), logLik(sarar_model_extended)),
  n       = c(
    length(residuals(sar_model_extended)),
    length(residuals(sdm_model_extended)),
    length(residuals(sarar_model_extended))
  ),
  moran_i = c(
    moran.test(residuals(sar_model_extended), spatial_weights_extended, zero.policy = TRUE)$estimate[["Moran I statistic"]],
    moran.test(residuals(sdm_model_extended), spatial_weights_extended, zero.policy = TRUE)$estimate[["Moran I statistic"]],
    moran.test(residuals(sarar_model_extended), spatial_weights_extended, zero.policy = TRUE)$estimate[["Moran I statistic"]]
  ),
  moran_p = c(
    moran.test(residuals(sar_model_extended), spatial_weights_extended, zero.policy = TRUE)$p.value,
    moran.test(residuals(sdm_model_extended), spatial_weights_extended, zero.policy = TRUE)$p.value,
    moran.test(residuals(sarar_model_extended), spatial_weights_extended, zero.policy = TRUE)$p.value
  )
) |>
  mutate(across(where(is.numeric), ~round(., 4)))

model_comparison_extended
```

```{r}
stargazer(
  model_comparison_extended,
  type = "html",
  title = "Spatial Model Comparison",
  summary = FALSE,
  rownames = FALSE,
  digits = 3,
  out = "figures/model_comparison_extended.html"
)
```

```{r}
# Is SDM significantly better than SAR?
LR.Sarlm(sdm_model_extended, sar_model_extended)
```

```{r}
# Is SARAR significantly better than SAR?
LR.Sarlm(sarar_model_extended, sar_model_extended)
```

```{r}
anova(sdm_model_extended, sarar_model_extended)
```

## Merge Crime and Officer Controls

`crime_county_avg` and `officers_county_avg` were built in `02_build_acs_ucr.qmd`;
they are joined here because this is the first point where `spatial_df_extended`
(built above, under "Spatial Weights Updated") exists to join them onto.

```{r}
spatial_df_extended <- spatial_df_extended |>
  left_join(crime_county_avg, by = "GEOID")

# Check merge success rate
spatial_df_extended |> st_drop_geometry() |>
  summarise(
    n_total = n(),
    n_missing_crime = sum(is.na(mean_violent_rate))
  )
```

```{r}
# Coverage check — how many counties have full 5-year coverage vs. partial?
crime_county_avg |> count(n_years_reported)
```

```{r}
# Coverage check
spatial_df_extended |> st_drop_geometry() |>
  summarise(
    n_total          = n(),
    n_with_crime     = sum(!is.na(mean_violent_rate)),
    n_missing_crime  = sum(is.na(mean_violent_rate)),
    pct_coverage     = scales::percent(n_with_crime / n_total, accuracy = 0.1),
    pct_missing      = scales::percent(n_missing_crime / n_total, accuracy = 0.1)
  )
```

```{r}
# Checking if coverage is associated with population 
spatial_df_extended |> st_drop_geometry() |>
  mutate(has_crime_data = !is.na(mean_violent_rate)) |>
  group_by(has_crime_data) |>
  summarise(
    n           = n(),
    mean_pop    = mean(total_pop, na.rm = TRUE),
    median_pop  = median(total_pop, na.rm = TRUE),
    .groups = "drop"
  )
```

```{r}
# Merge
spatial_df_extended <- spatial_df_extended |>
  left_join(officers_county_avg, by = "GEOID")

spatial_df_extended |> st_drop_geometry() |>
  summarise(
    n_total = n(),
    n_with_officers = sum(!is.na(mean_officers_per_1000)),
    pct_coverage = scales::percent(n_with_officers / n_total, accuracy = 0.1)
  )
```

```{r}
spatial_df_extended |> st_drop_geometry() |>
  summarise(
    missing_both    = sum(is.na(mean_violent_rate) & is.na(mean_officers_per_1000)),
    missing_crime_only = sum(is.na(mean_violent_rate) & !is.na(mean_officers_per_1000)),
    missing_officers_only = sum(!is.na(mean_violent_rate) & is.na(mean_officers_per_1000))
  )
```

```{r}
spatial_df_extended |> st_drop_geometry() |>
  summarise(
    n_total = n(),
    n_complete_both = sum(!is.na(mean_violent_rate) & !is.na(mean_officers_per_1000)),
    n_removed = n_total - n_complete_both,
    pct_removed = scales::percent(n_removed / n_total, accuracy = 0.1)
  )
```

### Distributions

```{r}
# all 4 variables have been log transformed
spatial_df_extended |> st_drop_geometry() |>
  select(log_pop_den, mean_violent_rate, mean_property_rate, mean_officers_per_1000) |>
  pivot_longer(everything()) |>
  ggplot(aes(x = value)) +
  geom_histogram(bins = 40) +
  facet_wrap(~name, scales = "free")
```

## Models with Controls

```{r}
# Filter predictors
spatial_df_full <- spatial_df |>
  left_join(crime_county_avg,    by = "GEOID") |>
  left_join(officers_county_avg, by = "GEOID") |>
  filter(!if_any(c(p_black, p_hisp, p_foreign, med_income, gini, log_pop_den,
                    med_home_val, p_renter, mean_violent_rate, mean_property_rate,
                    mean_officers_per_1000),
                  is.na))

cat("Counties retained:", nrow(spatial_df_full), "of", nrow(spatial_df), "\n")
```

```{r}
spatial_weights_full <- build_spatial_weights(spatial_df_full)
```

### 9. OLS with controls

```{r}
ols_model_full <- lm(
  full_formula,
  data = spatial_df_full |> st_drop_geometry()
)

summary(ols_model_full)
```

```{r}
car::vif(ols_model_full)
```

### Lagrange Multiplier Tests

```{r}
lm_tests_full <- lm.LMtests(
  ols_model_full,
  spatial_weights_full,
  test = "all",
  zero.policy = TRUE
)

summary(lm_tests_full)
```

### 10. SARAR with controls, no threshold

```{r}
sarar_model_full <- sacsarlm(
  full_formula,
  data    = spatial_df_full |> st_drop_geometry(),
  listw   = spatial_weights_full,
  zero.policy = TRUE
)

summary(sarar_model_full)
```

```{r}
moran.test(residuals(sarar_model_full), spatial_weights_full, zero.policy = TRUE)
```

### Moran I’s

```{r}
moran.test(residuals(sarar_model_full), spatial_weights_full, zero.policy = TRUE)
```

### 10b. Re-fit SARAR on new sample, no controls, no threshold

```{r}
sarar_model_old_on_new_sample <- sacsarlm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + med_income +
    gini + med_home_val + p_renter + log_pop_den,
  data    = spatial_df_full |> st_drop_geometry(),
  listw   = spatial_weights_full,
  zero.policy = TRUE
)
summary(sarar_model_old_on_new_sample)
```

```{r}
# Correlation between predictors
spatial_df_full |> st_drop_geometry() |>
  select(p_black, med_home_val, mean_property_rate, mean_violent_rate, mean_officers_per_1000) |>
  cor(use = "complete.obs")
```

### 11. Final Model, with 2500 Threshold

```{r}
spatial_df_full_2500 <- spatial_df |>
  filter(total_pop >= 2500) |>
  left_join(crime_county_avg,    by = "GEOID") |>
  left_join(officers_county_avg, by = "GEOID") |>
  filter(!if_any(c(p_black, p_hisp, p_foreign, med_income, gini, log_pop_den,
                    med_home_val, p_renter, mean_violent_rate, mean_property_rate,
                    mean_officers_per_1000), is.na))

spatial_weights_full_2500 <- build_spatial_weights(spatial_df_full_2500)
```

```{r}
lm_tests_2500 <- lm.LMtests(
  lm(full_formula,
     data = spatial_df_full_2500 |> st_drop_geometry()),
  spatial_weights_full_2500, test = "all", zero.policy = TRUE
)
summary(lm_tests_2500)
```

```{r}
sarar_model_final <- sacsarlm(
  full_formula,
  data    = spatial_df_full_2500 |> st_drop_geometry(),
  listw   = spatial_weights_full_2500,
  zero.policy = TRUE
)
summary(sarar_model_final)
```

```{r}
moran.test(residuals(sarar_model_final), spatial_weights_full_2500, zero.policy = TRUE)
```

#### Spatial Effects

```{r}
sarar_impacts <- impacts(sarar_model_final, listw = spatial_weights_full_2500,
                          zero.policy = TRUE, R = 200)   # R = number of simulation draws for SEs

summary(sarar_impacts, zstats = TRUE)
```

```{r}
sarar_impacts_summary <- summary(sarar_impacts, zstats = TRUE)
print(sarar_impacts_summary)
```
