---
title: "Robustness Checks"
format: html
---

## Population Threshold

```{r}
# Benefit: how many influential points fall below the various thresholds? 
cooks_d <- cooks.distance(ols_model_extended) 
influential_geoids <- spatial_df |> st_drop_geometry() |>
  filter(!if_any(c(p_black, p_hisp, p_foreign, med_income, gini, log_pop_den,
                    med_home_val, p_renter), is.na)) |>
  slice(which(cooks_d > 4 / length(cooks_d))) |>
  pull(GEOID)

spatial_df |>
  st_drop_geometry() |>
  filter(GEOID %in% influential_geoids) |>
  summarise(
    below_2500  = sum(total_pop < 2500),
    below_5000  = sum(total_pop < 5000),
    below_10000 = sum(total_pop < 10000),
    total_influential = n()
  )
```

```{r}
# Cost: how many of the total counties would be dropped at each threshold
spatial_df |> st_drop_geometry() |>
  summarise(
    n_total = n(),
    below_2500  = sum(total_pop < 2500),
    below_5000  = sum(total_pop < 5000),
    below_10000 = sum(total_pop < 10000)
  )
```

```{r}
# Threshold of 2500
threshold_summary_2500 <- bind_rows(
  spatial_df |> st_drop_geometry() |>
    summarise(
      group       = "All counties",
      n           = n(),
      below_2500  = sum(total_pop < 2500),
      pct         = scales::percent(below_2500 / n, accuracy = 0.1)
    ),
  spatial_df |> st_drop_geometry() |>
    filter(GEOID %in% influential_geoids) |>
    summarise(
      group       = "Influential counties (Cook's D > 4/n)",
      n           = n(),
      below_2500  = sum(total_pop < 2500),
      pct         = scales::percent(below_2500 / n, accuracy = 0.1)
    )
)

threshold_summary_2500
```

```{r}
# Threshold of 5000
threshold_summary_5000 <- bind_rows(
  spatial_df |> st_drop_geometry() |>
    summarise(
      group       = "All counties",
      n           = n(),
      below_5000  = sum(total_pop < 5000),
      pct         = scales::percent(below_5000 / n, accuracy = 0.1)
    ),
  spatial_df |> st_drop_geometry() |>
    filter(GEOID %in% influential_geoids) |>
    summarise(
      group       = "Influential counties (Cook's D > 4/n)",
      n           = n(),
      below_5000  = sum(total_pop < 5000),
      pct         = scales::percent(below_5000 / n, accuracy = 0.1)
    )
)

threshold_summary_5000
```

### Rebuilding dataset and spatial weights

#### Threshold = 5000

```{r}
# Population threshold: 5,000
spatial_df_5k <- spatial_df |> filter(total_pop >= 5000)
cat("Counties retained (threshold = 5,000):", nrow(spatial_df_5k), "of", nrow(spatial_df), "\n")
```

```{r}
weights_5k <- build_spatial_weights(spatial_df_5k)
```

#### Threshold = 2500

```{r}
# Population threshold = 2500
spatial_df_2500 <- spatial_df |> filter(total_pop >= 2500)
cat("Counties retained (threshold = 2,500):", nrow(spatial_df_2500), "of", nrow(spatial_df), "\n")
```

```{r}
weights_2500 <- build_spatial_weights(spatial_df_2500)
```

### 4 and 5 OLS with Thresholds

```{r}
# Models
ols_full <- lm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + 
    med_income + gini + med_home_val + p_renter + log_pop_den,
  data = spatial_df |> st_drop_geometry()
)

ols_2500 <- lm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + 
    med_income + gini + med_home_val + p_renter + log_pop_den,
  data = spatial_df_2500 |> st_drop_geometry() 
)

ols_5000 <- lm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + 
    med_income + gini + med_home_val + p_renter + log_pop_den,
  data = spatial_df_5k |> st_drop_geometry()
)

# extract_model() is defined once in 00_setup.qmd and reused across the repo
# Comparison table
comparison_wide <- bind_rows(
  extract_model(ols_full,  "Full sample"),
  extract_model(ols_2500,  "Threshold: 2,500+"),
  extract_model(ols_5000,  "Threshold: 5,000+")
) |>
  mutate(estimate_label = paste0(
    round(estimate, 3),
    case_when(
      p.value < 0.001 ~ "***",
      p.value < 0.01  ~ "**",
      p.value < 0.05  ~ "*",
      TRUE ~ ""
    )
  )) |>
  select(model, term, estimate_label) |>
  pivot_wider(names_from = model, values_from = estimate_label)

# R² and n table
model_stats <- tibble(
  model  = c("Full sample", "Threshold: 2,500+", "Threshold: 5,000+"),
  adj_r2 = c(glance(ols_full)$adj.r.squared, glance(ols_2500)$adj.r.squared, glance(ols_5000)$adj.r.squared),
  n      = c(nobs(ols_full), nobs(ols_2500), nobs(ols_5000))
)

comparison_wide
```

```{r}
model_stats
```

```{r}
shared_labels <- c(
  "Percent Black", "Percent Hispanic", "Percent foreign-born",
  "Median household income", "Gini coefficient", "Median home value",
  "Percent renter-occupied", "Log population density"
)

stargazer(
  ols_full, ols_2500, ols_5000,
  type = "text",
  title = "Extended OLS Model: Full Sample vs. Population Thresholds",
  column.labels = c("Full sample", "2,500+ threshold", "5,000+ threshold"),
  dep.var.labels = "Log(Surveillance Index per 100k + 1)",
  covariate.labels = shared_labels,
  digits = 3,
  omit.stat = c("f", "ser"),
  notes = "* p<0.05; ** p<0.01; *** p<0.001",
  notes.append = FALSE,
  out = "figures/extended_ols_comparisons_table.html"
)
```

```{r}
stargazer(
  ols_full, ols_2500, ols_5000,
  type = "html",
  title = "Extended OLS Model: Full Sample vs. Population Thresholds",
  column.labels = c("Full sample", "2,500+ threshold", "5,000+ threshold"),
  dep.var.labels = "Log(Surveillance Index per 100k + 1)",
  covariate.labels = shared_labels,
  digits = 3,
  omit.stat = c("f", "ser"),
  notes = "* p<0.05; ** p<0.01; *** p<0.001",
  notes.append = FALSE,
  out = "figures/extended_ols_comparisons_table.html"
)
```

### 11b. SARAR, no controls, isolates control effect at 2,500+

```{r}
sarar_model_no_controls <- sacsarlm(
  log1p(weighted_index_per100k) ~ p_black + p_hisp + p_foreign + med_income +
    gini + med_home_val + p_renter + log_pop_den,
  data    = spatial_df_full_2500 |> st_drop_geometry(),
  listw   = spatial_weights_full_2500,
  zero.policy = TRUE
)
summary(sarar_model_no_controls)
```

### 12. 5000 Threshold Robustness Check

```{r}
# Dataset and weights
spatial_df_full_5000 <- spatial_df |>
  filter(total_pop >= 5000) |>
  left_join(crime_county_avg,    by = "GEOID") |>
  left_join(officers_county_avg, by = "GEOID") |>
  filter(!if_any(c(p_black, p_hisp, p_foreign, med_income, gini, log_pop_den,
                    med_home_val, p_renter, mean_violent_rate, mean_property_rate,
                    mean_officers_per_1000), is.na))

cat("Counties retained (5,000+ threshold):", nrow(spatial_df_full_5000), "\n")
```

```{r}
weights_full_5000 <- build_spatial_weights(spatial_df_full_5000)
```

```{r}
# LM tests
lm_tests_5000 <- lm.LMtests(
  lm(full_formula,
     data = spatial_df_full_5000 |> st_drop_geometry()),
  weights_full_5000, test = "all", zero.policy = TRUE
)
summary(lm_tests_5000)
```

```{r}
# SARAR model
sarar_model_5000 <- sacsarlm(
  full_formula,
  data    = spatial_df_full_5000 |> st_drop_geometry(),
  listw   = weights_full_5000,
  zero.policy = TRUE
)
summary(sarar_model_5000)
```

```{r}
moran.test(residuals(sarar_model_5000), weights_full_5000, zero.policy = TRUE)
```

#### Comparison

```{r}
spatial_comparison_final <- bind_rows(
  extract_spatial_model(sarar_model_full,  "Full sample"),
  extract_spatial_model(sarar_model_final, "2,500+ (primary)"),
  extract_spatial_model(sarar_model_5000,  "5,000+ (robustness)")
) |>
  mutate(
    estimate_label = paste0(
      signif(estimate, 3),
      case_when(
        p_value == "< 0.0005" ~ "***",
        as.numeric(p_value) < 0.01  ~ "**",
        as.numeric(p_value) < 0.05  ~ "*",
        TRUE ~ ""
      )
    )
  ) |>
  select(model, term, estimate_label) |>
  pivot_wider(names_from = model, values_from = estimate_label)

# Model-level stats
model_level_final <- tibble(
  model  = c("Full sample", "2,500+ (primary)", "5,000+ (robustness)"),
  rho    = c(sarar_model_full$rho, sarar_model_final$rho, sarar_model_5000$rho),
  AIC    = c(AIC(sarar_model_full), AIC(sarar_model_final), AIC(sarar_model_5000)),
  n      = c(nobs(sarar_model_full), nobs(sarar_model_final), nobs(sarar_model_5000))
)

spatial_comparison_final
```

```{r}
model_level_final
```

## State and Federal Agencies Robustness Check

### 13. All agencies robustness check - SARAR with controls, 2,500+ threshold, all agencies

```{r}
atlas_clean_all_agencies <- atlas |>
  relocate(state, .before = state_abb) |>
  mutate(
    state = str_to_title(state),
    county = case_when(
      state == "Virginia" & county == "Manassas" & agency == "Manassas Park City Police Department" ~ "Manassas Park City",
      TRUE ~ county
    )
  ) |>
  left_join(corrections |> select(state, county, correct_county, correct_state),
            by = c("state", "county"), relationship = "many-to-many") |>
  mutate(
    county = coalesce(correct_county, county),
    state  = coalesce(correct_state, state)
  ) |>
  select(-correct_county, -correct_state)

cat("Records (all agencies):", nrow(atlas_clean_all_agencies), "\n")
```

```{r}
cat("Records (primary, local only):", nrow(atlas_clean), "\n")
```

```{r}
atlas_county_all <- atlas_clean_all_agencies |>
  mutate(
    county_clean = str_to_title(
      str_remove(county,
        regex(" County$| Parish$| Borough$| City And Borough$| Census Area$| Municipality$| Municipio$| Municipality County$| Islands?$",
              ignore_case = TRUE))
    )
  ) |>
  left_join(fips_xwalk, by = c("state" = "state_name", "county_clean" = "county_name")) |>
  left_join(tech_weights, by = "technology") |>
  mutate(weight = replace_na(weight, 1)) |>
  filter(!is.na(GEOID)) |>
  group_by(GEOID) |>
  summarise(
    state              = first(state),
    county             = first(county),
    n_records          = n(),
    n_agencies         = n_distinct(agency),
    n_tech_types       = n_distinct(technology),
    raw_weighted_index = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )

cat("atlas_county_all rows:", nrow(atlas_county_all), "\n")
```

```{r}
analysis_df_all <- acs |>
  left_join(atlas_county_all |> st_drop_geometry() |> select(GEOID, n_records, n_agencies, n_tech_types, raw_weighted_index),
            by = "GEOID") |>
  mutate(
    across(c(n_records, n_agencies, n_tech_types, raw_weighted_index), ~ replace_na(., 0)),
    weighted_index_per100k = raw_weighted_index / total_pop * 100000
  )

cat("analysis_df_all rows:", nrow(analysis_df_all), "\n")
```

```{r}
spatial_df_all <- analysis_df_all |>
  filter(!st_is_empty(geometry)) |>
  filter(!is.na(weighted_index_per100k))

cat("spatial_df_all rows:", nrow(spatial_df_all), "\n")
```

```{r}
spatial_df_full_all <- spatial_df_all |>
  left_join(crime_county_avg,    by = "GEOID") |>
  left_join(officers_county_avg, by = "GEOID") |>
  filter(total_pop >= 2500) |>
  filter(!if_any(c(p_black, p_hisp, p_foreign, med_income, gini, log_pop_den,
                    med_home_val, p_renter, mean_violent_rate, mean_property_rate,
                    mean_officers_per_1000), is.na))

cat("Counties retained (all agencies, 2,500+):", nrow(spatial_df_full_all), "\n")
```

```{r}
weights_full_all <- build_spatial_weights(spatial_df_full_all)
```

```{r}
sarar_model_all_agencies <- sacsarlm(
  full_formula,
  data    = spatial_df_full_all |> st_drop_geometry(),
  listw   = weights_full_all,
  zero.policy = TRUE
)
summary(sarar_model_all_agencies)
```

```{r}
moran.test(residuals(sarar_model_all_agencies), weights_full_all, zero.policy = TRUE)
```

```{r}
screenreg(
  list(
    "Final model (local agencies only)"  = sarar_model_final,
    "Robustness (all agencies included)" = sarar_model_all_agencies
  ),
  digits = 3, include.se = FALSE
)
```

```{r}
# Most direct check: does atlas_clean_all_agencies contain ANY state/federal agency records?
atlas_clean_all_agencies |> filter(lea_type %in% problem_types) |> nrow()
```

## Testing Neighbourhood Matrix

```{r}
# Average number of neighbours per county, for your final model's spatial weights
neighbour_counts <- card(spatial_weights_full_2500$neighbours)   # card() gives the neighbour count for each region

summary(neighbour_counts)   # min, max, median, mean
```

```{r}
table(card(spatial_weights_full_2500$neighbours))
```

```{r}
cat("Average number of neighbours per county (queen contiguity):", round(mean(neighbour_counts), 2), "\n")
```

```{r}
cat("Range:", min(neighbour_counts), "to", max(neighbour_counts), "\n")
```

```{r}
cat("Isolated counties (0 neighbours):", sum(neighbour_counts == 0), "\n")
```

```{r}
neighbour_comparison <- tibble(
  sample = c("Full sample", "2,500+ threshold", "5,000+ threshold"),
  mean_neighbours = c(
    mean(card(spatial_weights_extended$neighbours)),
    mean(card(spatial_weights_full_2500$neighbours)),
    mean(card(weights_full_5000$neighbours))   # adjust object name to match yours
  ),
  n_isolated = c(
    sum(card(spatial_weights_extended$neighbours) == 0),
    sum(card(spatial_weights_full_2500$neighbours) == 0),
    sum(card(weights_full_5000$neighbours) == 0)
  )
) |>
  mutate(mean_neighbours = round(mean_neighbours, 2))

neighbour_comparison
```

### K-NN Alternative

#### Selecting K

```{r}
# knn_listw() and scan_k() are defined once in 00_setup.qmd
coords_2500 <- st_coordinates(st_point_on_surface(spatial_df_full_2500))
k_values <- c(4, 6, 8, 10, 12, 15)
model_data_2500 <- spatial_df_full_2500 |> st_drop_geometry()

# SAR scan (faster) used first to get a rough AIC-optimal k...
k_results <- map_dfr(k_values, scan_k, coords = coords_2500, data = model_data_2500,
                      formula = full_formula, fit_fun = lagsarlm)
k_results
```

```{r}
# ...then confirmed with the full SARAR specification
k_results_sarar <- map_dfr(k_values, scan_k, coords = coords_2500, data = model_data_2500,
                            formula = full_formula, fit_fun = sacsarlm)
k_results_sarar
```

#### 14. k = 6

```{r}
weights_knn6 <- knn_listw(coords_2500, k = 6)

sarar_model_knn6 <- sacsarlm(
  full_formula,
  data    = model_data_2500,
  listw   = weights_knn6,
  zero.policy = TRUE
)

summary(sarar_model_knn6)
```

```{r}
moran.test(residuals(sarar_model_knn6), weights_knn6, zero.policy = TRUE)
```

#### 15. k = 12

```{r}
weights_knn12 <- knn_listw(coords_2500, k = 12)

sarar_model_knn12 <- sacsarlm(
  full_formula,
  data  = model_data_2500,
  listw = weights_knn12,
  zero.policy = TRUE
)

summary(sarar_model_knn12)
```

```{r}
moran.test(residuals(sarar_model_knn12), weights_knn12, zero.policy = TRUE)
```

#### K-NN Comparison

```{r}
screenreg(
  list(
    "SARAR (queen)"  = sarar_model_final,
    "SARAR (KNN=6)"  = sarar_model_knn6,
    "SARAR (KNN=12)" = sarar_model_knn12
  ),
  digits = 3,
  include.se = FALSE
)
```

```{r}
htmlreg(
  list(
    "SARAR (queen)"  = sarar_model_final,
    "SARAR (KNN=6)"  = sarar_model_knn6,
    "SARAR (KNN=12)" = sarar_model_knn12
  ),
  digits = 3,
  include.se = FALSE,
  file = "figures/neighbour_structure_comparison.html"
)
```

```{r}
neighbour_diagnostics <- tibble(
  specification = c("SARAR (queen)", "SARAR (KNN=6)", "SARAR (KNN=12)"),
  mean_neighbours = c(
    mean(card(spatial_weights_full_2500$neighbours)),
    mean(card(weights_knn6$neighbours)),
    mean(card(weights_knn12$neighbours))
  ),
  AIC = c(
    AIC(sarar_model_final),
    AIC(sarar_model_knn6),
    AIC(sarar_model_knn12)
  ),
  moran_i_residuals = c(
    moran.test(residuals(sarar_model_final), spatial_weights_full_2500, zero.policy = TRUE)$estimate[1],
    moran.test(residuals(sarar_model_knn6), weights_knn6, zero.policy = TRUE)$estimate[1],
    moran.test(residuals(sarar_model_knn12), weights_knn12, zero.policy = TRUE)$estimate[1]
  ),
  moran_p_value = c(
    moran.test(residuals(sarar_model_final), spatial_weights_full_2500, zero.policy = TRUE)$p.value,
    moran.test(residuals(sarar_model_knn6), weights_knn6, zero.policy = TRUE)$p.value,
    moran.test(residuals(sarar_model_knn12), weights_knn12, zero.policy = TRUE)$p.value
  )
) |>
  mutate(across(where(is.numeric), ~round(., 4)))

neighbour_diagnostics
```
